### 2022-08-19 ersteops/templates/printpdf/rendered_template.tex
add medic signature

\begin{document}
\fontfamily{lmss}\selectfont
    % Include Background in ./prescript/media/media/template_v1.pdf
    % \AddToShipoutPictureBG{\ifthenelse{\isodd{\value{page}}}{\includegraphics{laam_template}}{\includegraphics{laam_template}}}
    % Define page content
    %\textsf{\large{
    %\begin{changemargin}{1.5cm}{1.2cm}
        %\begin{enumerate}
            %
            %bla!
        %\end{enumerate}
    %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
    %    \textbf{Consulta \#:} 40
    % }
    % }}}
        % Indicaciones Extra
        % \begin{enumerate}
        %     \textbf{Indicaciones Extra: \\ } 
        % \end{enumerate}
    %\end{changemargin}
    %}}
    % \begin{picture}(1,0.77272727)%
    %     %Consulta    
    % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
    %    \textbf40
    % }
    % }}}
    % \end{picture}
% \begingroup%
%   \makeatletter%
%   \providecommand\color[2][]{%
%     \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
%     \renewcommand\color[2][]{}%
%   }%
%   \providecommand\transparent[1]{%
%     \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
%     \renewcommand\transparent[1]{}%
%   }%
%   \providecommand\rotatebox[2]{#2}%
%   \newcommand\scaleInNode[1][1]{\tikzset{execute at begin node={\normalsize\larger[#1]}}}
%   \newcommand*\fsize{\dimexpr\f@size pt\relax}%
%   \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
%   \ifx\svgwidth\undefined%
%     \setlength{\unitlength}{792bp}%
%     \ifx\svgscale\undefined%
%       \relax%
%     \else%
%       \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
%     \fi%
%   \else%
%     \setlength{\unitlength}{\svgwidth}%
%   \fi%
%   \global\let\svgwidth\undefined%
%   \global\let\svgscale\undefined%
%   \makeatother%
%   \begin{picture}(1,0.77272727)%
%     \lineheight{1}%
%     \setlength\tabcolsep{0pt}%
%     \put(0,0){\includegraphics[width=\unitlength,page=1]{laam_template}}%

%     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
%     %    \textbf{Consulta \#:} 40
%     % }
%     % }}}
%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 40 }\end{tabular}}}}%
% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 40 }\end{tabular}}}}%
%    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ M011 }\end{tabular}}}}%
%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ SOPORTE }\end{tabular}}}}%
%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-002 }\end{tabular}}}}%

@@

\begingroup%
  \makeatletter%
  \providecommand\color[2][]{%
    \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
    \renewcommand\color[2][]{}%
  }%
  \providecommand\transparent[1]{%
    \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
    \renewcommand\transparent[1]{}%
  }%
  \providecommand\rotatebox[2]{#2}%
  \newcommand*\fsize{\dimexpr\f@size pt\relax}%
  \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
  \ifx\svgwidth\undefined%
    \setlength{\unitlength}{782.27360219bp}%
    \ifx\svgscale\undefined%
      \relax%
    \else%
      \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
    \fi%
  \else%
    \setlength{\unitlength}{\svgwidth}%
  \fi%
  \global\let\svgwidth\undefined%
  \global\let\svgscale\undefined%
  \makeatother%
  \begin{picture}(1,0.77245213)%
    \lineheight{1}%
    \setlength\tabcolsep{0pt}%
    \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_1}}%

    %Folio
    \put(0.91336785,0.68838718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 40\end{tabular}}}}%

    \put(0.42638971,0.73960084){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 11\end{tabular}}}}%
    \put(0.43014479,0.72364315){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont M011\end{tabular}}}}%
   	\put(0.33829987,0.69381105){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont SOPORTE\end{tabular}}}}%
    \put(0.39132267,0.67728521){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-002\end{tabular}}}}%

@@

\begingroup%
  \makeatletter%
  \providecommand\color[2][]{%
    \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
    \renewcommand\color[2][]{}%
  }%
  \providecommand\transparent[1]{%
    \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
    \renewcommand\transparent[1]{}%
  }%
  \providecommand\rotatebox[2]{#2}%
  \newcommand*\fsize{\dimexpr\f@size pt\relax}%
  \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
  \ifx\svgwidth\undefined%
    \setlength{\unitlength}{782.27360219bp}%
    \ifx\svgscale\undefined%
      \relax%
    \else%
      \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
    \fi%
  \else%
    \setlength{\unitlength}{\svgwidth}%
  \fi%
  \global\let\svgwidth\undefined%
  \global\let\svgscale\undefined%
  \makeatother%
  \begin{picture}(1,0.77245213)%
    \lineheight{1}%
    \setlength\tabcolsep{0pt}%
    \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_2}}%
    %Impresion diagnostica
    \put(0.02433222,0.72271027){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    %Tratamiento
    \put(0.02377709,0.34714045){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
    %Derivacion
    \put(0.56751227,0.6911999){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont []\end{tabular}}}}%
    \put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.60035291,0.65502334){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.60169212,0.63688865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
    \put(0.54544497,0.61971664){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    %Finalizacion
    \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.6223905,0.54640692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.54203741,0.50578489){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Dr.Chapatin\end{tabular}}}}%
    \put(0.59900976,0.48543641){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont XXX-XXXX-XXX\end{tabular}}}}%
    \put(0.53065814,0.46522944){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cacharpo\end{tabular}}}}%
    \put(0.55816754,0.44488927){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont El Operador\end{tabular}}}}%
    %\put(0.92413649,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X4 }}\end{tabular}}}}%
    \put(0.65327278,0.35657174){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ NA }}\end{tabular}}}}%
    %\put(0.77324116,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X3 }}\end{tabular}}}}%
    %\put(0.76701121,0.33763243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X2 }}\end{tabular}}}}%
    %\put(0.66004404,0.33814317){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{☑︎}}\end{tabular}}}}%

>>>>

\begin{document}
\fontfamily{lmss}\selectfont
    % Include Background in ./prescript/media/media/template_v1.pdf
    % \AddToShipoutPictureBG{\ifthenelse{\isodd{\value{page}}}{\includegraphics{laam_template}}{\includegraphics{laam_template}}}
    % Define page content
    %\textsf{\large{
    %\begin{changemargin}{1.5cm}{1.2cm}
        %\begin{enumerate}
            %
            %bla!
        %\end{enumerate}
    %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
    %    \textbf{Consulta \#:} 49
    % }
    % }}}
        % Indicaciones Extra
        % \begin{enumerate}
        %     \textbf{Indicaciones Extra: \\ } 
        % \end{enumerate}
    %\end{changemargin}
    %}}
    % \begin{picture}(1,0.77272727)%
    %     %Consulta    
    % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
    %    \textbf49
    % }
    % }}}
    % \end{picture}
% \begingroup%
%   \makeatletter%
%   \providecommand\color[2][]{%
%     \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
%     \renewcommand\color[2][]{}%
%   }%
%   \providecommand\transparent[1]{%
%     \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
%     \renewcommand\transparent[1]{}%
%   }%
%   \providecommand\rotatebox[2]{#2}%
%   \newcommand\scaleInNode[1][1]{\tikzset{execute at begin node={\normalsize\larger[#1]}}}
%   \newcommand*\fsize{\dimexpr\f@size pt\relax}%
%   \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
%   \ifx\svgwidth\undefined%
%     \setlength{\unitlength}{792bp}%
%     \ifx\svgscale\undefined%
%       \relax%
%     \else%
%       \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
%     \fi%
%   \else%
%     \setlength{\unitlength}{\svgwidth}%
%   \fi%
%   \global\let\svgwidth\undefined%
%   \global\let\svgscale\undefined%
%   \makeatother%
%   \begin{picture}(1,0.77272727)%
%     \lineheight{1}%
%     \setlength\tabcolsep{0pt}%
%     \put(0,0){\includegraphics[width=\unitlength,page=1]{laam_template}}%

%     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
%     %    \textbf{Consulta \#:} 49
%     % }
%     % }}}
%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 49 }\end{tabular}}}}%
% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 49 }\end{tabular}}}}%
%    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ M011 }\end{tabular}}}}%
%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ ASISTENCIA BASICA }\end{tabular}}}}%
%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-006 }\end{tabular}}}}%

@@

\begingroup%
  \makeatletter%
  \providecommand\color[2][]{%
    \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
    \renewcommand\color[2][]{}%
  }%
  \providecommand\transparent[1]{%
    \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
    \renewcommand\transparent[1]{}%
  }%
  \providecommand\rotatebox[2]{#2}%
  \newcommand*\fsize{\dimexpr\f@size pt\relax}%
  \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
  \ifx\svgwidth\undefined%
    \setlength{\unitlength}{782.27360219bp}%
    \ifx\svgscale\undefined%
      \relax%
    \else%
      \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
    \fi%
  \else%
    \setlength{\unitlength}{\svgwidth}%
  \fi%
  \global\let\svgwidth\undefined%
  \global\let\svgscale\undefined%
  \makeatother%
  \begin{picture}(1,0.77245213)%
    \lineheight{1}%
    \setlength\tabcolsep{0pt}%
    \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_1}}%
    %\put(0.31336785,0.38838718){\includegraphics[scale=1]{test_image}}%
    %\put(0.78960956,0.24450476){\includegraphics[scale=0.5]{client_signature}}%

    %Folio
    \put(0.91336785,0.68838718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 49\end{tabular}}}}%

    \put(0.42638971,0.73960084){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 11\end{tabular}}}}%
    \put(0.43014479,0.72364315){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont M011\end{tabular}}}}%
   	\put(0.33829987,0.69381105){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont ASISTENCIA BASICA\end{tabular}}}}%
    \put(0.39132267,0.67728521){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-006\end{tabular}}}}%

@@

\begingroup%
  \makeatletter%
  \providecommand\color[2][]{%
    \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
    \renewcommand\color[2][]{}%
  }%
  \providecommand\transparent[1]{%
    \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
    \renewcommand\transparent[1]{}%
  }%
  \providecommand\rotatebox[2]{#2}%
  \newcommand*\fsize{\dimexpr\f@size pt\relax}%
  \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
  \ifx\svgwidth\undefined%
    \setlength{\unitlength}{782.27360219bp}%
    \ifx\svgscale\undefined%
      \relax%
    \else%
      \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
    \fi%
  \else%
    \setlength{\unitlength}{\svgwidth}%
  \fi%
  \global\let\svgwidth\undefined%
  \global\let\svgscale\undefined%
  \makeatother%
  \begin{picture}(1,0.77245213)%
    \lineheight{1}%
    \setlength\tabcolsep{0pt}%
    \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_2}}%

    \put(0.78960956,0.16450476){\includegraphics[scale=0.5]{client_signature}}%
    \put(0.64203741,0.20450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%

    \put(0.78960956,0.46450476){\includegraphics[scale=0.5,frame]{signature_medic}}%
    \put(0.78960956,0.44450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Firma Médico\end{tabular}}}}%

    %Impresion diagnostica
    \put(0.02433222,0.72271027){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    %Tratamiento
    \put(0.02377709,0.34714045){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
    %Derivacion
    \put(0.56751227,0.6911999){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont []\end{tabular}}}}%
    \put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.60035291,0.65502334){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.60169212,0.63688865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
    \put(0.54544497,0.61971664){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    %Finalizacion
    \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%\

    \put(0.6223905,0.54640692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
    \put(0.54203741,0.50578489){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Dr.Chapatin\end{tabular}}}}%
    \put(0.59900976,0.48543641){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont XXX-XXXX-XXX\end{tabular}}}}%
    \put(0.53065814,0.46522944){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cacharpo\end{tabular}}}}%
    \put(0.55816754,0.44488927){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont El Operador\end{tabular}}}}%
    %\put(0.92413649,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X4 }}\end{tabular}}}}%
    \put(0.65327278,0.35657174){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ NA }}\end{tabular}}}}%
    %\put(0.77324116,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X3 }}\end{tabular}}}}%
    %\put(0.76701121,0.33763243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X2 }}\end{tabular}}}}%
    %\put(0.66004404,0.33814317){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{☑︎}}\end{tabular}}}}%
